### 2021-08-13 sections/model_overview/main.tex
Add info about asymmetric replicator dynamics

\section{Overview of game theoretic model}

@@

Both queueing systems follow a queueing model that has two waiting spaces for 
individuals. 
The first waiting zone is where the individuals queue right before receiving 
their service and has a capacity of \( N - C \), where \(N\) is the total 
capacity of the waiting space and \(C\) is the number of servers. 
The second waiting zone is where the individuals, that are sent from the 
distributor, remain until they are allowed to enter the first waiting zone.
The second waiting zone has a capacity of \(M\) and no servers.

>>>>

\section{Overview of game theoretic model} \label{sec:model_overview}

@@

Both queueing systems follow a queueing model that has two waiting spaces for 
individuals. 
The first waiting zone is where the individuals queue right before receiving 
their service and has a capacity of \( N - C \), where \(N\) is the total 
capacity of the waiting space and \(C\) is the number of servers. 
The second waiting zone is where the individuals, that are sent from the 
distributor, stay until they are allowed to enter the first waiting zone.
The second waiting zone has a capacity of \(M\) and no servers.
